---
title: "Explant infection experiments"
output: github_document
---
Explant infection overview:

Explants are infected at 2E6 pfu/ml and then washed after 20-24hr. After washing, media is replaced with  media containing 0.6ug/ml PHA. PHA-containing media is replaced with plain media after ~24hr.

Luciferase levels in collected supernatent are assesed with the Promega nano-glo kit.


# Explant Infection 001:

Pre-incubate virus (vNL_sNLuc.6ATRi.B.Bal.ecto) with exosomes before adding to explants:

  * Concentrations: 1E5 and 1E4 exosomes per pfu
  
  * Exosomes used: SE and HE
  
We also included explant only and virus only controls.



```{r infection 001}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(plyr)
library(dplyr)
library(plater)
library(ggplot2)
library(stringr)

options(scipen = 999)

explant_infection_001<-read_plate("../Explant_infection_001/20Sept16_infection001_layout_and_data.csv")


explant_infection_001<-explant_infection_001%>%
  mutate(Day = str_trim(Day, side = "both"))

#function for ordering day factors nicely:
orderDays<- function(exp_df){
  factor(exp_df$Day, levels = c("1","1 wash","3","6","8","10","13","15","17","20"))
}

explant_infection_001$Day<-orderDays(explant_infection_001)

#Map the exo per pfu values so they will match the later experiments

explant_infection_001$Exo_per_pfu <- mapvalues(explant_infection_001$Exo_per_pfu, from = c("1.0E+04","1.0E+05"), to = c("1E4","1E5"))




ggplot(explant_infection_001, aes(x = Day, y = log10(RLU)))+
  geom_point(aes(color = Treatment,shape = Exo_per_pfu),size = 3)+
  geom_line(aes(group = interaction(Treatment, Exo_per_pfu),color = Treatment))+
ggtitle("Explant infection 001")
  
```


#Explant infection 002

* Same conditions as 001

```{r infection 002}
explant_infection_002<-read_plate("../Explant_infection_002/04Oct16_infection002_layout_and_data.csv")

#order the factors nicely
explant_infection_002$Day<-orderDays(explant_infection_002)


#Map the exo per pfu values so they will match the later experiments
explant_infection_002$Exo_per_pfu <- mapvalues(explant_infection_002$Exo_per_pfu, from = c("1.0E+04","1.0E+05"), to = c("1E4","1E5"))



ggplot(explant_infection_002, aes(x = Day, y =log10 (RLU)))+
  geom_point(aes(color = Treatment,shape = Exo_per_pfu),size = 3)+
  geom_line(aes(group = interaction(Treatment, Exo_per_pfu),color = Treatment))+
  ggtitle("Explant infection 002")
  
```

#Explant Infection 003:

* Concentrations: 1E5 and 1E4 exosomes per pfu, 1:50 seminal sup.
  
* Exosomes used: SE and HE

This was a two part experiment: 

Pre-incubate virus (vNL_sNLuc.6ATRi.B.Bal.ecto) with exosomes OR seminal sup before adding to explants:

  * Controls = explants only and explants with virus that was incubated alone at 37C for ~1hr (like the virus + exos)

Pre-incubate explants with exosomes OR seminal sup before virus is added.
  
  * Controls = explants only and explants infected with virus that was kept in the fridge for ~1hr.

PROTOCOL DEVIATIONS: 

* I forgot to remove the PHA-containing media on day 2, so it wasn't replaced with new media until day 3.

* There were 4 explants in the "pre-incubate explants with 1E5 HE" condition.


```{r infection 003, echo = FALSE}


#I made two verions of plate layout and data files, the 2nd one seems to work better so I'm using that here. previous committed scripts have the first one too.


explant_infection_003_plate1<-read_plate("../Explant_infection_003/11Oct16_infection003_plate1_layout_and_data.csv")


explant_infection_003_plate2<-read_plate("../Explant_infection_003/11Oct16_infection003_plate2_layout_and_data.csv")



explant_infection_003<-rbind(explant_infection_003_plate1,explant_infection_003_plate2)


explant_infection_003$Day <- orderDays(explant_infection_003)



#Map the exo per pfu values so they will match the later experiments

explant_infection_003$Exo_per_pfu <- mapvalues(explant_infection_003$Exo_per_pfu, from = c("1.0E+04","1.0E+05"), to = c("1E4","1E5"))


#split the data into two experiments, but include the explant_only control in both (condition code 3).

#One experiment was virus or sup pre-incubated with exos(condition codes: 1,2(control),5,6,7), the other was explants pre-incubated with exos(condition numbers: 4(control),8-13). 



```


*Reminder*: In the plot below,"virus only" means that the explants were infected with virus that had been incubating (with no exos) for 1hr at 37C.


```{r plot virus+ exo preinc, echo = FALSE}

#filter for just the virus + exo preinc conditions and include the controls (so numbers 1-7)
virus_preinc_003<- explant_infection_003 %>%
  filter(Code <8 )



ggplot(virus_preinc_003, aes(x = Day, y = log10(RLU)))+
  geom_point(aes(color = Treatment, shape = Exo_per_pfu),size = 3)+
  geom_line(aes(group = interaction(Treatment, Exo_per_pfu), color = Treatment))+
  ggtitle("Virus pre-incubated with exosomes or seminal sup")

```


*Reminder*: In the plot below, "virus only" means that the explants were infected with virus that had been in the fridge (with no exos) for 1hr.


```{r plot explant + exo preinc, echo = FALSE}

#filter for just the explant + exo preinc conditions and include the explant_only control(number 3). Number 9 is the virus only control for the pre-incubated explant + exos experiment (analogous to #2 in the virus + exo experiment)

explant_preinc_003<-explant_infection_003%>%
  filter(Code ==3|Code >=8)

ggplot(explant_preinc_003, aes(x = Day, y = log10(RLU)))+
  geom_point(aes(color = Treatment, shape = Exo_per_pfu),size = 3)+
  geom_line(aes(group = interaction(Treatment, Exo_per_pfu), color = Treatment))+
  ggtitle("Explants pre-incubated with exosomes or seminal sup")
```

#Explant Infection 004:

* Concentrations: 1E5,1E4, 1E3 and 5E4 exosomes per pfu, 1:50 seminal sup.
  
* Exosomes used: SE and HE

* Only did virus (vNL_sNLuc.6ATRi.B.Bal.ecto) and exosome/sup preincubation (no exos + explant preinc)

```{r infection004, message = FALSE, echo = FALSE}

explant_infection_004_plate1<-read_plate("../Explant_infection_004/25OCt16_infection004_plate1_layout_and_data.csv")


explant_infection_004_plate2<-read_plate("../Explant_infection_004/25OCt16_infection004_plate2_layout_and_data.csv")


explant_infection_004<-rbind(explant_infection_004_plate1, explant_infection_004_plate2)


#order the factors nicely
explant_infection_004$Day <- orderDays(explant_infection_004)


#for some reason the exo per pfu shows up as actual numbers, not scientific notation, even though it is is sci not in excel... This is a plater BUG

explant_infection_004$Exo_per_pfu <- mapvalues(explant_infection_004$Exo_per_pfu, from = c("10000","100000","1000","50000"), to = c("1E4","1E5","1E3","5E4"))


ggplot(explant_infection_004, aes(x = Day, y = log10(RLU)))+
  geom_point(aes(color = Treatment,shape = Exo_per_pfu),size = 3)+
  geom_line(aes(group = interaction(Treatment, Exo_per_pfu),color = Treatment))+
  ggtitle("Explant infection 004")



```


#Explant Infection 005:

* Concentrations: 1E5,1E4, 1E3 and 5E4 exosomes per pfu, 1:50 seminal sup.
  
* Exosomes used: SE and HE

* Only did virus (vNL_sNLuc.6ATRi.B.Bal.ecto) and exosome/sup preincubation (no exos + explant preinc)

PROTOCOL DEVIATIONS: 

* During virus wash off I skipped a well so conditions 8-11 were off by one on the spin plate. I abandoned those pellets since they got mixed up and started using a new set of wells for  the washes for those conditions.


```{r infection005, message = FALSE, echo = FALSE}

explant_infection_005_plate1<-read_plate("../Explant_infection_005/14Nov16_infection005_plate1_layout_and_data.csv")


explant_infection_005_plate2<-read_plate("../Explant_infection_005/14Nov16_infection005_plate2_layout_and_data.csv")


explant_infection_005<-rbind(explant_infection_005_plate1, explant_infection_005_plate2)


#order the factors nicely
explant_infection_005$Day <- orderDays(explant_infection_005)

#for some reason the exo per pfu shows up as actual numbers, not scientific notation, even though it is is sci not in excel... plater bug!

explant_infection_005$Exo_per_pfu <- mapvalues(explant_infection_005$Exo_per_pfu, from = c("10000","100000","1000","50000"), to = c("1E4","1E5","1E3","5E4"))



ggplot(explant_infection_005, aes(x = Day, y = log10(RLU)))+
  geom_point(aes(color = Treatment,shape = Exo_per_pfu),size = 3)+
  geom_line(aes(group = interaction(Treatment, Exo_per_pfu),color = Treatment))+
  ggtitle("Explant infection 005")

```

#Explant Infection 006:

* Concentrations: 1E5,1E4, 1E3 and 5E4 exosomes per pfu, 1:50 seminal sup.
  
* Exosomes used: SE and HE

* Only did virus (vNL_sNLuc.6ATRi.B.Bal.ecto) and exosome/sup preincubation (no exos + explant preinc)

* Did 2 reps for each condition

PROTOCOL DEVIATIONS: 

* Did not collect sups for conditions 1, 5, 9, 2, 6 and 10 on day 10 (by mistake) but did replace media.


```{r infection006, message = FALSE, echo = FALSE}

explant_infection_006_plate1<-read_plate("../Explant_infection_006/23Nov16_infection006_plate1_layout_and_data.csv")


explant_infection_006_plate2<-read_plate("../Explant_infection_006/23Nov16_infection006_plate2_layout_and_data.csv")


explant_infection_006_plate3<-read_plate("../Explant_infection_006/23Nov16_infection006_plate3_layout_and_data.csv")


explant_infection_006<-rbind(explant_infection_006_plate1, explant_infection_006_plate2,explant_infection_006_plate3)


#order the factors nicely
explant_infection_006$Day <- orderDays(explant_infection_006)


#fix sci not weirdness due to plateR bug( all are in sci notation in excel but plater converts some of them to regular notation...)

explant_infection_006$Exo_per_pfu <- mapvalues(explant_infection_006$Exo_per_pfu, from = c("5.00E+04","1.00E+04","100000","1000","50000"), to = c("5E4",
"1E4","1E5","1E3","5E4"))

```

First check how the replicates look
```{r checking replicates, message = FALSE, echo = FALSE}
ggplot(explant_infection_006, aes(x = Day, y = log10(RLU)))+
  geom_point(aes(color = Treatment,shape = Exo_per_pfu),size = 3)+
  facet_wrap(~Treatment+Exo_per_pfu)+
  ggtitle("Explant infection 006")

```

```{r avg replicates, message = FALSE, echo = FALSE}

avgReps_explant_infection_006<-
  explant_infection_006 %>%
  group_by(Treatment, Exo_per_pfu,Day,Condition, Code)%>%
  summarise(RLU = mean(RLU))
```

```{r plot avg reps, message = FALSE, echo = FALSE}
ggplot(avgReps_explant_infection_006, aes(x = Day, y = log10(meanRLU)))+
  geom_point(aes(color = Treatment,shape = Exo_per_pfu),size = 3)+
  geom_line(aes(group = interaction(Treatment, Exo_per_pfu),color = Treatment))+
  ggtitle("Explant infection 006 (avg of 2 replicates)")
```


```{r compilation setup, message = FALSE, echo = FALSE}

#This is getting complicated to look at so I'm going to combine the results of multiple experiments to get a better idea of what's going on.

#combining the results of the virus-preinc-with-exos experiments (not the explants with exos one, so just the "virus_preinc_003" df from explant infection 003)


#also note that for exp 006, I did replicates of each condition, so the data here are averaged reps.

compiled <- list(avgReps_explant_infection_006,explant_infection_005,explant_infection_004,explant_infection_002,explant_infection_001, virus_preinc_003)

names(compiled) <- c("explant_infection_006","explant_infection_005","explant_infection_004","explant_infection_002","explant_infection_001", "virus_preinc_003")


compiled <- bind_rows(compiled, .id = "Experiment")



compiled$Exo_per_pfu <- factor(compiled$Exo_per_pfu, levels = c("no_exo_no_virus","no_exo","1E3","1E4","5E4","1E5"))
```


Compilations of results from multiple experiments (not including 006) arranged in a variety of ways:



```{r compilation plots, message = FALSE, echo = FALSE, fig.height = 7, fig.width = 12}

ggplot(compiled, aes(x = Day, y = log10(RLU)))+
  geom_point(aes(color = Experiment, shape = Treatment),size = 3)+
  geom_line(aes(group = interaction(Treatment, Exo_per_pfu, Experiment),color = Experiment))+
  facet_wrap(~Exo_per_pfu)+
  ggtitle("Virus pre-incubated with exosomes: faceted by Exo_per_pfu")

```

```{r compilation subset for LV}

#Lucia wants a day 8 data for all the experiments, so I will subset and export that here:
#remember that is is only a compilation of the results from the virus-preinc-with-exos experiments (not the explants with exos data  from explant infection 003)

#also note that for exp 006, I did replicates of each condition, so the data here are averaged reps.

day8_compiled <- compiled %>%
  filter(Day ==  "8")

write.csv(day8_compiled, file = "day8_compiled_explant_Bal_preinc_with_exos.csv", row.names = FALSE)

```