---
title: "Explant infection experiments"
output: github_document
---

Explant infection 001 had the following conditions:

1) Pre-incubate 10^4 SE + virus together, then add to explants

2) Virus only

3) Explants only

4) Pre-incubate 10^4 Hela exos + virus together, then add

5) Pre-incubate 10^5 SE + virus together, then add to explants

6) pre-inc 10^5 Hela exos + virus

The virus concentration was 2E6 pfu/ml


```{r echo=FALSE, message=FALSE, warning=FALSE}

library(plyr)
library(dplyr)
library(plateR)
library(ggplot2)
library(stringr)



explant_infection_001<-read_plate("../Explant_infection_001/20Sept16_plate_layout_and_data.csv")


explant_infection_001<-explant_infection_001%>%
  mutate(Day = str_trim(Day, side = "both"))


#order the factors nicely
explant_infection_001$Day <- factor(explant_infection_001$Day, levels = c("1","1 wash","3","6","8","10","13","15","17","20"))


ggplot(explant_infection_001, aes(x = Day, y = RLU))+
  geom_point(aes(color = Treatment,shape = Exo_per_pfu),size = 3)+
  geom_line(aes(group = interaction(Treatment, Exo_per_pfu),color = Treatment))+
  scale_y_log10()+
  ggtitle("Explant_infection_001")
  

```

Another way of looking at it:


```{r echo=FALSE, message=FALSE, warning=FALSE}

ggplot(explant_infection_001, aes(x = Day, y = RLU))+
  geom_point(aes(color = Treatment),size = 3)+
  geom_line(aes(group = interaction(Treatment, Exo_per_pfu),color = Treatment))+
  scale_y_log10()+
  facet_wrap(~Exo_per_pfu)+
  ggtitle("Explant_infection_001")