---
title: "Explant titrations"
output:
  md_document:
    variant: markdown_github
---
## Explant Titrations


### Goal

Titrate lot1 of vNL_sNLuc_6ATRi.B.Bal.ecto based on the kinetics of RA and KW's virus; "Bal26 lot1", at the concentration that they use for infection experiments (dilution factor of 17.91, I think...)
 
## Titration 001

This is a plot of luciferase production over days 1 - 14 for multiple conditions. The "Hladik Bal lot1" virus is vNL_sNLuc_6ATRi.B.Bal.ecto made by Greg Mize

* The conditions are in the format virus type:dilution factor. 

* Day 1 supernatent still contains input virus. 1 wash is still day 1 but after the explants have been washed to remove input virus. 

* Hladik Bal26 lot1 with a dilution factors of 34.38 or 17.19 look closest to RA/KW's virus.



```{r echo=FALSE, message=FALSE, warning=FALSE}

library(dplyr)
library(plateR)
library(ggplot2)

#Read in data collected 07June16 from day1-day14. I put the raw data into a file with the meta data in plateR format

titer001_day1_14<-read_plate("../Explant_titration_001/07June16_plate_layout_and_data.csv")


titer001_day1_14$Day <- factor(titer001_day1_14$Day,levels = c("1","1 wash","3","7","10","14"))

ggplot(titer001_day1_14, aes(x = Day, y = RLU))+
  geom_point(aes(color = Condition))+
  geom_line(aes(group = Condition, color = Condition))+
  scale_y_log10()
  
  


```

This is a plot of the luciferase over time from day1- 21 but we included fewer conditions based on the results from the first run of d1-14 with all conditions. 

* Hladik Bal26 lot1 with a dilution factor of 17.19 looks closest to Bal26 lot1.


```{r echo=FALSE, message=FALSE, warning=FALSE}




#Read in data collected 16June16 from day1-day21.We only ran conditions "A","C",and "D" and Bal lot 26. I put the raw data into a file with the meta data in plateR format. 

titer001_day1_21ACD<-read_plate("../Explant_titration_001/16June16_plate_layout_and_data.csv")


titer001_day1_21ACD$Day <- factor(titer001_day1_21ACD$Day,levels = c("1 wash","3","7","10","14","17","21"))

ggplot(titer001_day1_21ACD, aes(x = Day, y = RLU))+
  geom_point(aes(color = Condition))+
  geom_line(aes(group = Condition, color = Condition))+
  scale_y_log10()
```

## Titration 002

Lucia set up a second titration experiment on 14June16. 

* Hladik Bal with a dilution factor of 25 matches the kinetics of Bal26 lot1, but I'm not sure why they are so different from all the other conditions. 


```{r echo=FALSE, message=FALSE, warning=FALSE}
#Read in data from 07July16 nanoluc assay.

titer002_day1_21<-read_plate("../Explant_titration_002/06July16_plate_layout_and_data.csv")


titer002_day1_21$Day <- factor(titer002_day1_21$Day,levels = c("1","1 wash","3","6","8","10","13","15","17", "21"))

ggplot(titer002_day1_21, aes(x = Day, y = RLU))+
  geom_point(aes(color = Condition))+
  geom_line(aes(group = Condition, color = Condition))+
  scale_y_log10()
```

## Conclusions

* Based on three nanoluc assays from two different titrations, the dilution factors for Hladik Bal lot1 virus that resulted in kinetics that were closest to Bal26 lot1 were a range between ~9 to 25.

## Caveats

* The "No virus" control was kind of high for the second titration.

* The Bal26 lot1 and Hladik Bal lot1 lines, both with dilution factor of 17.91 were very low compared to all the other dilutions


