---
title: "Explant titrations"
date:
author:
output: github_document
  
---



### Goal

Titrate lot2 of vNL_sNLuc_6ATRi.B.Bal.ecto based on the kinetics of RA and KW's virus; "Bal26 lot1", at the concentration that they use for infection experiments (1.92E6 pfu/ml)
 
## Titration 001

This is a plot of luciferase production over days 1 - 14 for multiple conditions. The "Hladik Bal lot2" virus is vNL_sNLuc_6ATRi.B.Bal.ecto lot2 made by Greg Mize.

* Day 1 supernatent still contains input virus. 1 wash is still day 1 but after the explants have been washed to remove input virus. 

* Hladik Bal26 lot2 with pfu/ml of 3.64E5 or 7.27E5 (dil. factors 68.76, 34.38) look closest to RA/KW's virus.



```{r echo=FALSE, message=FALSE, warning=FALSE}

library(plyr)
library(dplyr)
library(plateR)
library(ggplot2)
library(stringr)


#Read in data collected 07June16 from day1-day14. I put the raw data into a file with the meta data in plateR format

titer001_day1_14<-read_plate("../Explant_titration_001/07June16_plate_layout_and_data.csv")

#order the factors nicely
titer001_day1_14$Day <- factor(titer001_day1_14$Day,levels = c("1","1 wash","3","7","10","14"))

#make the pfu/ml into factors, then rename the factors so the number ones are in sci not.

titer001_day1_14$pfu_per_ml <- factor(titer001_day1_14$pfu_per_ml)


titer001_day1_14$pfu_per_ml <- mapvalues (titer001_day1_14$pfu_per_ml,from =c(1450000,1920000,2880000,364000,5810000,727000), to = c("1.45E6","1.92E6","2.88E6","3.64E5","5.81E6","7.27E5"))
                                                                         
ggplot(titer001_day1_14, aes(x = Day, y = RLU))+
  geom_point(aes(color = pfu_per_ml, shape = Virus),size = 3)+
  geom_line(aes(group = pfu_per_ml, color = pfu_per_ml))+
  scale_shape_manual(values = c("Hladik Bal lot2" = 16, "Bal26 lot1" = 1, "No virus" = 4))+
  scale_y_log10()
  
  


```
----
This is a plot of the luciferase over time from day1- 21 but we included fewer conditions based on the results from the first run of d1-14 with all conditions. 

* Hladik Bal26 lot2 with a pfu/ml of 7.27E5 (dil. factor of 34.38) looks closest to Bal26 lot1.


```{r echo=FALSE, message=FALSE, warning=FALSE}


#Read in data collected 16June16 from day1-day21.We only ran conditions "A","C",and "D" and Bal lot 26. I put the raw data into a file with the meta data in plateR format. 

titer001_day1_21ACD<-read_plate("../Explant_titration_001/16June16_plate_layout_and_data.csv")


titer001_day1_21ACD$Day <- factor(titer001_day1_21ACD$Day,levels = c("1 wash","3","7","10","14","17","21"))


titer001_day1_21ACD$pfu_per_ml <- mapvalues (titer001_day1_21ACD$pfu_per_ml,from =c(1920000,1450000, 2880000,727000), to = c("1.92E6","1.45E6","2.88E6","7.27E5"))


#make the dilution factor character so it plays nicely with other dfs that don't non-numeric entries for dil factor ("no virus")

titer001_day1_21ACD$Dilution_factor <-as.character(titer001_day1_21ACD$Dilution_factor)
                   
ggplot(titer001_day1_21ACD, aes(x = Day, y = RLU))+
  geom_point(aes(color = pfu_per_ml, shape = Virus),size = 3)+
  geom_line(aes(group = pfu_per_ml, color =pfu_per_ml))+
  scale_shape_manual(values = c("Hladik Bal lot2" = 16, "Bal26 lot1" = 1, "No virus" = 4))+
  scale_y_log10()



```

## Titration 002

Lucia set up a second titration experiment on 14June16. 

* Hladik Bal with a dilution factor of 5.4E5 (dil. factor 46.3) matches the kinetics of Bal26 lot1.


```{r echo=FALSE, message=FALSE, warning=FALSE}
#Read in data from 07July16 nanoluc assay.

titer002_day1_21<-read_plate("../Explant_titration_002/06July16_plate_layout_and_data.csv")


titer002_day1_21$Day <- factor(titer002_day1_21$Day,levels = c("1","1 wash","3","6","8","10","13","15","17", "21"))



titer002_day1_21$pfu_per_ml <- mapvalues (titer002_day1_21$pfu_per_ml,from =c(1600000,1920000, 1e+06,2400000, 540000), to = c(
  "1.6E6", "1.92E6","1E6","2.4E6","5.4E5"))


ggplot(titer002_day1_21, aes(x = Day, y = RLU))+
  geom_point(aes(color = pfu_per_ml, shape = Virus),size = 3)+
  geom_line(aes(group = pfu_per_ml, color =pfu_per_ml))+
  scale_shape_manual(values = c("Hladik Bal lot2" = 16, "Bal26 lot1" = 1, "No virus" = 4))+
  scale_y_log10()
```

## Titration 003


On 12July I started third titration testing four different concentrations of pfu/ml : 3E5, 5E5, 1E6,2E6 and 3E6. I also included two "No virus" conditions; one well that was separated from the others by a whole column of wells and another that was in the same column as the other conditions. 

```{r echo=FALSE, message=FALSE, warning=FALSE}



titer003_day1_20<-read_plate("../Explant_titration_003/04Aug16_whiteplate_layout_and_data.csv")


titer003_day1_20$Day <- factor(titer003_day1_20$Day,levels = c("1","1 wash","3","6","8","10","13","15","17", "20"))




titer003_day1_20$pfu_per_ml <- mapvalues (titer003_day1_20$pfu_per_ml,from =c("1.92E+06", "3.00E+06","5.00E+05","3.00E+05", "1.00E+06","2.00E+06"), to = c(
  "1.92E6","3E6","3E5","5E5","1E6","2E6"))



ggplot(titer003_day1_20, aes(x = Day, y = RLU))+
  geom_point(aes(color = pfu_per_ml, shape = Virus),size = 3)+
  geom_line(aes(group = pfu_per_ml, color = pfu_per_ml))+
  scale_shape_manual(values = c("Hladik Bal lot2" = 16, "Bal26 lot1" = 1, "Media only background cntl" = 4, "No virus1" = 3, "No virus2" = 6))+
  scale_y_log10()+
  scale_color_discrete(name = "PFU/ml or Treatment")

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

#combine all the data frames
compiled <- list(titer001_day1_21ACD, titer001_day1_14, titer002_day1_21, titer003_day1_20)

names(compiled) <- c("titer001_day1_21ACD","titer001_day1_14","titer002_day1_21","titer003_day1_20")


compiled <- bind_rows(compiled, .id = "Experiment")
```

## Summary


Here is a plot of just Bal26 lot 1 kinetics in the different experiments. Note that I ran sups from the first titration twice; one up to day14 and once for all the days.

```{r echo=FALSE, message=FALSE, warning=FALSE}

#filter for just Bal 26 lot1 and for no virus

Bal26<-filter(compiled, Virus != "Hladik Bal lot2" & Virus != "Media only background cntl")

Bal26$Day<-factor(Bal26$Day, levels = c("1", "1 wash","3", "6","7","8","10","13","14","15","17","20","21"))



ggplot(Bal26, aes(x = Day, y = RLU))+
  geom_point(aes(color = Experiment, shape = Virus),size = 3)+
  geom_line(aes(group = interaction(Experiment,Virus), color = Experiment))+
  scale_y_log10()+
  scale_shape_manual(values = c("Bal26 lot1" = 1, "No virus" = 4, "No virus1" = 4, "No virus2" = 4 ))+
  ggtitle("Bal26 lot 1 and No virus controls")



```

Here are the Bal26 lot 1 kinetics next to the concentration of Hladik Bal lot2 that matched most closely. I am only showing the results from titration001 sups from all days.

* Bal26 lot1 is always at 1.92E6 PFU/ml

 


```{r echo=FALSE, message=FALSE, warning=FALSE}

Bal26andClosest <- compiled %>%
filter(pfu_per_ml == "7.27E5"|pfu_per_ml==
         "2.88E6"|pfu_per_ml =="5.4E5" |pfu_per_ml == "2E6"| pfu_per_ml =="3E6")

Bal26andClosest <- rbind(Bal26andClosest, Bal26)

Bal26andClosest<- Bal26andClosest%>%
  filter(!grepl("No virus1?2?", Virus))%>%
  filter(Experiment != "titer001_day1_14")



Bal26andClosest$Day<-factor(Bal26andClosest$Day, levels = c("1", "1 wash","3", "6","7","8","10","13","14","15","17","20","21"))


ggplot(Bal26andClosest, aes(x = Day, y = RLU))+
  geom_point(aes(color = Experiment, shape = pfu_per_ml),size = 3)+
  geom_line(aes(group = interaction(Experiment,pfu_per_ml), color = Experiment))+
  scale_y_log10()+
  ggtitle("Bal26 lot1 and closest concentrations of Hladik Bal lot2")
```


